Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-14 Manuscript/proof_outline.tex
remove some blue/todos

Extending Lemma~\ref{l1}, we would like to write a finite union of
members of a semi-ring as a finite union of disjoint sets.

\todo[inline]{Is this section going into too much detail?}

@@

\begin{definition}\label{def:content}
  For some set $\alpha$, let $\mathcal H \subseteq 2^\alpha$
  {\color{blue}and call any $m : \mathcal H \to [0,\infty]$ a
    content.}
  \begin{enumerate}
  \item $m$ is called additive if for $\mathcal K \subseteq_f \mathcal
    H$ pariwise disjoint and $\bigcup_{K \in \mathcal K} K \in
    \mathcal H$, we have $m \Big(\bigcup_{K \in \mathcal K} K \Big) =
    \sum_{K \in \mathcal K} m(K)$. If the same holds for\footnote {We
      write $A \subseteq_c B$ if $A$ is a countable subset of
      $B$.}$\mathcal K \subseteq_c \mathcal H$ pariwise disjoint, we
    say that $m$ is $\sigma$-additive.
  \item The set-function $m$ is called sub-additive if for $\mathcal K
    \subseteq_f \mathcal H$ and $\bigcup_{K \in \mathcal K} K \in
    \mathcal H$, we have $m \Big(\bigcup_{K \in \mathcal K} K \Big)
    \leq \sum_{K \in \mathcal K} m(K)$. (Note that elements of
    $\mathcal K$ need not be disjoint.) Here, $\sigma$-sub-additivity
    is defined in the obvious way using $\mathcal K\subseteq_c
    \mathcal H$.
  \item If $m(A) \leq m(B)$ for $A\subseteq B$ and $A,B\in\mathcal H$,
    we say that $m$ is monotone.
  \item If $\mathcal H$ is a $\sigma$-algebra and $m$ is
    $\sigma$-additive {\color{blue} with $m(\emptyset) = 0$}, we call
    $m$ a measure.
  \item If $\mathcal H = 2^\alpha$ and $m$ is monotone and
    $\sigma$-sub-additive with $m(\emptyset)=0$, we call $m$ an outer
    measure.
  \end{enumerate}
\end{definition}

@@

\noindent
\xout{In these formalizations, we introduced $m(\emptyset)=0$ as a
  separate hypothesis with empty'. Note that this also follows
  formally from $m(\emptyset) = m(\emptyset \cup \emptyset) = 2
  m(\emptyset)$. However, since Finsets are assumed to have distinct
  elements, we cannot have ∅ twice in I.}

@@

\noindent
From the next lemma, we will need monotonicity and sub-additivity, as
well as $\sigma$-additive $\Rightarrow$ $\sigma$-sub-additive in the
proof of the Carathéodory extension,
Theorem~\ref{T:masseind}. {\color{blue}We do not show any details
  about its formalization here.}

>>>>

Extending Lemma~\ref{l1}, we would like to write a finite union of
members of a semi-ring as a finite union of disjoint sets\todo{Is this section going into too much detail?}.

@@

\begin{definition}\label{def:content}
  For some set $\alpha$, let $\mathcal H \subseteq 2^\alpha$
  and call any $m : \mathcal H \to [0,\infty]$ a
    content.
  \begin{enumerate}
  \item $m$ is called additive if for $\mathcal K \subseteq_f \mathcal
    H$ pariwise disjoint and $\bigcup_{K \in \mathcal K} K \in
    \mathcal H$, we have $m \Big(\bigcup_{K \in \mathcal K} K \Big) =
    \sum_{K \in \mathcal K} m(K)$. If the same holds for\footnote {We
      write $A \subseteq_c B$ if $A$ is a countable subset of
      $B$.}$\mathcal K \subseteq_c \mathcal H$ pariwise disjoint, we
    say that $m$ is $\sigma$-additive.
  \item The set-function $m$ is called sub-additive if for $\mathcal K
    \subseteq_f \mathcal H$ and $\bigcup_{K \in \mathcal K} K \in
    \mathcal H$, we have $m \Big(\bigcup_{K \in \mathcal K} K \Big)
    \leq \sum_{K \in \mathcal K} m(K)$. (Note that elements of
    $\mathcal K$ need not be disjoint.) Here, $\sigma$-sub-additivity
    is defined in the obvious way using $\mathcal K\subseteq_c
    \mathcal H$.
  \item If $m(A) \leq m(B)$ for $A\subseteq B$ and $A,B\in\mathcal H$,
    we say that $m$ is monotone.
  \item If $\mathcal H$ is a $\sigma$-algebra and $m$ is
    $\sigma$-additive with $m(\emptyset) = 0$, we call
    $m$ a measure.
  \item If $\mathcal H = 2^\alpha$ and $m$ is monotone and
    $\sigma$-sub-additive with $m(\emptyset)=0$, we call $m$ an outer
    measure.
  \end{enumerate}
\end{definition}

@@

@@

\noindent
From the next lemma, we will need monotonicity and sub-additivity, as
well as $\sigma$-additive $\Rightarrow$ $\sigma$-sub-additive in the
proof of the Carathéodory extension,
Theorem~\ref{T:masseind}. We do not show any details
  about its formalization here.
